Sparse spectral and $p$-finite element methods for partial differential equations on disk-slices and trapeziums

### 2019-05-14 papers/halfdisk/halfdisk.tex
Added comments

The motivation for this work is solving partial differential equations on sub-domains of the sphere. In particular, OPs in cartesian coordinates ($x$, $y$, and $z$) on a half-sphere  can be represented using two families of OPs on the half-disk, see \cite[Theorem 3.1]{olver2018orthogonal} for a similar construction of OPs on an arc in 2D.
%, where we would require $2n+1$ 3D OPs for each degree $n$, of which $n+1$ would be the $n+1$ degree $n$ OPs on the half-disk of the first family (polynomials in $x,y$) while the remaining $n$ OPs would be given by $z$ multiplied by the $n$ degree $n-1$ OPs on the half-disk of the second family. 
Constructing sparse spectral methods for surface PDEs on half-spheres, spherical caps, and spherical triangles is future work, and has applications in weather prediction \cite{staniforth2012horizontal}. Other extensions include a full $hp$-finite element method on sections of a disk, which has applications in fluids.

@@

@@

>>>>

The motivation for this work is solving partial differential equations on sub-domains of the sphere. In particular, OPs in cartesian coordinates ($x$, $y$, and $z$) on a half-sphere  can be represented using two families of OPs on the half-disk, see \cite[Theorem 3.1]{olver2018orthogonal} for a similar construction of OPs on an arc in 2D.
%, where we would require $2n+1$ 3D OPs for each degree $n$, of which $n+1$ would be the $n+1$ degree $n$ OPs on the half-disk of the first family (polynomials in $x,y$) while the remaining $n$ OPs would be given by $z$ multiplied by the $n$ degree $n-1$ OPs on the half-disk of the second family. 
Constructing sparse spectral methods for surface PDEs on half-spheres, spherical caps, and spherical triangles is future work, and has applications in weather prediction \cite{staniforth2012horizontal}. Other extensions include a full $hp$-finite element method on sections of a disk, which has applications in fluids \bstodo{Reference?}.

@@

\bstodoinline{N=100, k=200 in the example isn't converging to a solution, so need a new fig. Add in solution block norms fig  - what should RHSs be?}

@@

\bstodoinline{Add in solution block norms fig - what should RHSs be?}
